%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plasmati Graduate CV
% LaTeX Template
% Version 1.0 (24/3/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati (alessandro.plasmati@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creivecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template needs to be compiled with XeLaTeX.
% The main document font is called Fontin and can be downloaded for free
% from here: http://www.exljbris.com/fontin.html
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper,11pt]{extarticle} % Default font size and paper size

\usepackage{fontspec} % For loading fonts
\defaultfontfeatures{Mapping=tex-text}
% \setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin} % Main document font
% \fontspec{[FontAwesome.otf]}
\setmainfont[Path = ./Ubuntu/,  %% Optional; but UPDATE this if 
                                %% your font files are in a folder
 Extension = .ttf,
 UprightFont = *-Regular,
 BoldFont = *-Bold,
 ItalicFont = *-Italic,
 SmallCapsFont = *-Medium]
{Ubuntu}
\fontspec{[fontawesome-webfont.ttf]}

\usepackage{color}
\definecolor{primary}{rgb}{0.4, 0, 0.1}
\definecolor{secondary}{rgb}{0, 0, 0}

\usepackage{xunicode,xltxtra,url,parskip} % Formatting packages

\usepackage[usenames,dvipsnames]{xcolor} % Required for specifying custom colors

%\usepackage[big]{layaureo} % Margin formatting of the A4 page, an alternative to layaureo can be 
%\usepackage{fullpage}
\usepackage{geometry}
\geometry{a4paper,margin=0.40cm}
%\geometry{a4paper,left=20mm, top=20mm}
 %To reduce the height of the top margin uncomment: \addtolength{\voffset}{-1.3cm}

\usepackage{hyperref} % Required for adding links	and customizing them
\definecolor{linkcolour}{rgb}{0,0.4,0.5} % Link color
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour} % Set link colors throughout the document

\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{0pt}{0pt} % Spacing around sections

\usepackage{multicol}
\setlength{\columnsep}{0cm}

\usepackage{tabularx}

\usepackage{textcomp}

\usepackage{fontawesome}

\usepackage{enumitem}
\setlist[description]{%
  topsep=10pt,               % space before start / after end of list
  itemsep=1pt,               % space between items
%  font={\bfseries\sffamily\color{red}}, % if colour is needed
}

\def\arraystretch{1}
\renewcommand{\baselinestretch}{1.1}

\begin{document}

\pagestyle{empty} % Removes page numbering

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------
\begin{multicols}{3}

\normalsize  \faEnvelope\ {\href{samhitha.sriraman@sjsu.edu }{\  samhitha.sriraman@sjsu.edu}}\\
\normalsize \faPhone\ {\href{}{\  858 308 6462}}\\
\columnbreak
\normalsize\par{\centering{\huge\textsc{\textcolor{primary}{Samhitha Sriraman }}}\par} 
\par{\centering\normalsize {San Jose, California}\hfill\par}
\columnbreak
\raggedright\hfill\normalsize \faLinkedinSquare\ {\href{https://www.linkedin.com/in/samhithasrirama/}{\  LinkedIn}}\\
\end{multicols}
\vspace{-0.4 cm}
%----------------------------------------------------------------------------------------
%	SKILLS 
%----------------------------------------------------------------------------------------
 \vspace{+0.4cm} \section{\textcolor{primary}{\href{https://www.github.com/proffapt/bodhitree}{Technical Skills}}}

 \vspace{+0.2cm}

 \begin{tabular}{r|p{15cm}}
 \textsc{Languages} & Java/J2EE, Scala, JavaScript, MySQL, XML, HTML, Python, Node JS, Kafka\\
 \textsc{Technologies \&Frameworks}& Spring, Angular, Spring Boot, REST, Microservices, AWS, Jenkins, Git\\
 \textsc{DBMS} &  MySQL, Oracle DB, MongoDB, PostgreSQL\\
 \textsc{Project Management}& Agile, Scrum, Kanban, Waterfall, Jira,Project Lifecycle Management, Cross-functional Team Leadership, Stakeholder
Communication, Risk Mitigation, Budget Management\\
 % \textsc{Others} & Git, GitHub, GitLab, Proxmox, Backend Development, Web Browser Extension Development \\
 
 % -------- ToAdd but not confident enough -----------
 %  React.js, Data Structures and Algorithms
 % ----------
\end{tabular}



% ----------------------------------------------------------------------------------------
% 	EXPERIENCE
% ----------------------------------------------------------------------------------------
\vspace{+0.2cm}
\section{\textcolor{primary}{Experience}}
\vspace{+0.1cm}
% \fontsize{9}{12}\selectfont{

\begin{itemize}[leftmargin=0.55cm, rightmargin=0.2cm, label={\Large\textbullet}]

\item \textbf{Technical Program Manager| \href{}{University Of Chicago}} \hfill{\textit{Aug '23 - Present}} \\
- Led backend development and technical program management for a Spring-based financial platform, optimizing payment workflows for 5,000+ users.\newline
- Improved release efficiency by reducing deployment time by 25\% through Jenkins automation and Agile best practices, driving continuous integration and delivery.
\newline
- Built AI-driven risk assessment models at Phoenix AI, enhancing fraud detection and anomaly detection.
 \newline
- Designed and optimized RESTful APIs, reducing response times by 20\% through caching and  data modeling.\newline
- Mentored 5 junior engineers driving  50+ code reviews, improving code quality  and  team productivity by 20\%.

\item \textbf{Full Stack Engineer | \href{}{\textbf{NSEIT Ltd}
}} \hfill{\textit{April '21 - Jan '22}} \\
- Led a team of 5 engineers in developing BNX-Brunei Stock Exchange, increasing system reliability by 40\%.\newline
- Managed full stack development using Java, Spring Boot, Angular and React with Microservices reducing \newline transaction processing time by 30\%.\newline
- Spearheaded the design and implementation of 20+ front-end features, reducing page load time by 30\%.\newline
- Delivered high-priority financial modules, ensuring 100\% on-time delivery across 3 major releases.\newline
- Optimized MySQL databases, reducing query response times by 25\% and improving data throughput.\newline
- Implemented security layers for the web application using \textbf{Spring Security and JWT-based authentication,} ensuring \textbf{secure API access and user authentication.}


\item \textbf{Software Engineer | \href{}{\textbf{\textbf{Virtusa}}
}} \hfill{\textit{Jan '21 - Apr '21}} \\
- Liaised between clients and internal teams, ensuring alignment with project goals.\newline
- Managed project timelines and resources, ensuring on-time delivery and adherence to budget.\newline
- Migrated legacy systems to AWS/Docker, reducing costs by 40\% and boosting scalability.\newline
- Enhanced data retrieval by 20\% through MVC integration with Spring, addressing customer needs.
\item \textbf{Software Engineer | \href{}{\textbf{\textbf{Patterns Cognitive}}
}} \hfill{\textit{Oct '17 - Dec '20}} \\
-  \textbf{Led end-to-end software development lifecycle (SDLC) activities} for Tata Capital Financial Services, collaborating with cross-functional teams from \textbf{requirement gathering} and \textbf{system design} to \textbf{development, testing, and production deployment}, ensuring timely and efficient delivery of financial applications.\newline
- Designed and implemented a robust lease invoicing automation tool, converting client requirements into software solutions that \textbf{streamlined monthly invoice generation} for customers reducing manual intervention.\newline
- \textbf{Diagnosed and resolved data leakage issues,} optimizing backend data validation and error-handling mechanisms, which led to a \textbf{38\% improvement in application performance and data integrity.}\newline
- Developed and deployed AI/ML-based cheque processing automation for Mashreq Bank, leveraging machine learning models to \textbf{reduce processing time and errors by 20\%}, enhancing financial transaction accuracy.\newline
- Directed the implementation of automated workflows into outdated systems, increasing operational efficiency by processing 10,000+ transactions monthly with minimal errors.\newline}






\end{itemize}

% }
%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{\textcolor{primary}{Education}}
\vspace{+0.2cm}

  \textbf{San Jose state University}\hfill{\textit{\textbf{Dec 2025}}} \newline
  \textit{Master of Business Administration}\newline
    \textbf{Sastra University}\hfill{\textit{\textbf{June 2017}}} \newline
 \textit{Bachelor and Master of Technology, Electronics and Communication Systems}
\end{document}